{$\ch_2(\tf)$ Optimality Conditions for a Finite-time Horizon\thanksref{mytitlenote}}

### 2019-05-13 response.tex

\def\serkan#1{\textcolor{blue}{{#1}}}
\def\caleb#1{\textcolor{blue}{{#1}}}
\def\chris#1{\textcolor{blue}{{#1}}}
\def\serkanlast#1{\textcolor{blue}{{#1}}}

\title{Authors' Response to the Referee Comments}
\author{}
\date{}
\begin{document}
\maketitle

We thank the referees {for their detailed reading of the manuscript and their valuable comments}.
 We have incorporated the changes that the referees have suggested into the revised
manuscript.   We list below the referees' comments, followed by our responses, denoted by \serkan{\textsf{AR}}.

Also in the revised manuscripts, all the revisions  are highlighted by color blue for the referees to spot them easily.

@@

\section*{Referee \#1}%change this about referee #1

\begin{itemize}
\item My only concern is the fact that the term H2 is used on time-domain
function, which might be inappropriate from a mathematical point of
view?\\[1ex]
\serkan{\textsf{AR}: We agree with the referee that the term $H_2$ is associated with measure in the frequency domain. To clarify this point. we have added a footnote, Footnote 4 at the bottom of page 3, explaining the usage.
} 
\end{itemize}

@@

\section*{Referee \#2}

\begin{itemize}
\item The introduction of the paper does not allow to position the problem
accurately even though valuable elements of this positioning are given
in section 3.3. \\ [1ex]
\serkan{\textsf{AR}:  We thank the referee for pointing this out. We have added some of this discussion from Section 3.3 to Introduction now (the second to last paragraph in Introduction to help resolve this issue.}

\item Some particular application domains are cited in the beginning without
justification. \\[1ex]
\serkan{\textsf{AR}:  We have added citations.}  
\item What about the choice of the finite horizon tf ? \\ [1ex]
\serkan{\textsf{AR}: The choice of the finite horizon is really problem and application dependent; however the interpolation conditions hold for any $t_f$. We added a sentence right before Remark 3.2 to state this fact.}

\item Justify the choice of simple poles for the reduced order model. \\ [1ex]
\serkan{\textsf{AR}:  The choice of simple poles was motivated by the infinite horizon $\mathcal{H}_2$ optimal approximation problems and the corresponding interpolation, as in, for example, citations [3,6,7, 11,23] in the paper. Indeed, the interpolatory $\mathcal{H}_2$  approximation has been extended some specific nonlinear dynamical systems as well, such as 
\begin{itemize}
\item   P. Benner and T. Breiten, Interpolation-based $\mathcal{H}_2$-model reduction of
                  bilinear control systems, SIAM Journal on Matrix Analysis and Applications, 2012.
\item  G. Flagg and S. Gugercin,  Multipoint Volterra Series Interpolation and $\mathcal{H}_2$ Optimal Model Reduction of Bilinear Systems, SIAM Journal on Matrix Analysis and Applications, 2015.
\item P. Benner , P. Goyal, and S. Gugercin, $\mathcal{H}_2$-quasi-optimal model order reduction for quadratic-bilinear control systems, SIAM Journal on Matrix Analysis and Applications, 2018.
\end{itemize}
These nonlinear extensions also use the same assumptions. It is certainly theoretically possible that an optimal $\mathcal{H}_2$ reduced model can have repeated poles and interpolation conditions have been extended to this case as well: 
\begin{itemize}
\item P. van Dooren, K. Gallivan, and  P.-A. Absil, 
$\mathcal{H}_2$-Optimal Model Reduction with Higher-Order Poles,
	SIAM Journal on Matrix Analysis and Applications, 2010.
\end{itemize}
However, this is situation is rarely observed in practice and we chose to use simple poles. Also, we note that the full model can have repeated poles. The assumption is only on the reduced model.
}

\item What is the reference of the existing result given by Theorem 2.1 ? \\ [1ex]
\serkan{\textsf{AR}:  We have added the citations immediately after the theorem.}

\item Notation are not fixed in the paper. For example H'(s) is the
derivative of H with respect to s. This can be stated at the end of the
introduction section (with all other notations...)\\ [1ex]
\serkan{\textsf{AR}:  We have added a clarification for this notation immediately after Theorem 2.1, which corresponds to the first occurrence of $\bf{H}'(s)$ .}

\item  Section 2.2 : the 5 introduction lines are very important and can be
used to state the purpose of the paper. \\ [1ex]
\serkan{\textsf{AR}: These five lines state the purpose of infinite horizon optimal model reduction even though what we consider here, i.e., optimal model reduction on a finite horizon, has some similar difficulties. Following the referee's earlier suggestion (the first comment), we have added some more discussion about our approach to the introduction.}

\item section 3 : the first 5 lines are a "useless repetition" and can be
removed. \\ [1ex]
\serkan{\textsf{AR}:  We have removed these 5 lines and reorganized the beginning of section 3 }

\item Section 3 : lines 6 to 10 can be given as a Remark (important remark!)  \\ [1ex]
\serkan{\textsf{AR}:  We have followed  the referee's recommendation and list these lines as Remark 3.3 now. }

\item Remark 3.2 can be given after the proof of the main result and can be
a part of the discussion of the given result. \\[1ex]
\serkan{\textsf{AR}:  We have moved the remark after the proof as the referee suggested. }

\item Lemma 3.3 : "Let G(s) and Gr(s) be as defined in (3.5) and (3.7)"
instead of "Let G(s) and Gr(s) be as defined in (3.5) and (3.5)" \\ [1ex]
\serkan{\textsf{AR}:  We thank the referee for pointing out this issue. We have addressed it in the revised version.}

\item Page 8 : (3.18) is one equation no need to (3.19). \\ [1ex]
\serkan{\textsf{AR}:  We thank the referee for pointing out this issue. We have addressed it in the revised version.}

\item The computation of (3.18) is not clear. One can give more details
allowing to obtain such result. \\ [1ex]
\serkan{\textsf{AR}:   We have added more details after Equation (3.18) better explaining these computations.}

\item Sentence after (3.19) : "...in the parentheses in (3.18) and (3.19)"
instead of "...in the parentheses in (3.18) and (3.18)". \\[1ex]
\serkan{\textsf{AR}:  We thank the referee for pointing out this issue. We have addressed it in the revised version.}

\item 3.3 section can be a (concise) part of the introduction of the paper. \\[1ex]
\serkan{\textsf{AR}:  We thank the referee for the comment.  We believe that section 3.3 addresses the importance of the result. We believe that explaining the result after it is given is more appropriate and ti makes it more tangible for the reader.}

\item Section 4 : should state how to use the main result in constructing
the reduced order model which is not the case in the current version.\\
\serkan{\textsf{AR}:  This comment was not very clear to us.  Corollaries 4.1 and 4.2, which follow directly from the main result, explain how we are using the optimality conditions to construct the algorithm.  We were not sure what else the referee would like to see explained.}

\item The numerical examples try to show the "supremacy" of the proposed
result which is obviously not the case. Instead, it will be useful to
explain clearly the aim of each numerical experimentation before giving
a clear figure (with only one comparison aim at each time). The given
figures are almost indecipherable !\\[1ex]
\serkan{\textsf{AR}:  We thank the referee for pointing out the difficulties in reading the figures. We have not separated the figures into subplots, making the comparisons easier and hopefully making the figures more clear.
}

\textcolor{blue}{
We were not sure why the referee claimed that the proposed method outperformed the other methods. For every model and for every reduced order we have tried, FHIRKA has improved whatever initialization we have used. In some cases the improvements were dramatic in some cases less so. However regardless it has produced a lower error. We have excluded some $r$ values not because FHIRKA performed bad. It was simply because other methods has lead to very poor approximations that should not be used as an initialization.}

@@

\end{itemize}

\section*{Referee \#3}

\begin{itemize}
\item As stated in Remark 3.2, the optimality condition is not directly
expressed by H(s) and Hr(s), but by G(s) and Gr(s), defined by (3.5)
and (3.7).  The reviewer cannot find a physical interpretation of G(s)
and Gr(s).  The authors can comment on the interpretation.\\
\serkan{\textsf{AR}:  We thank the referee for this comment. We have addressed this issue on the revised version  and added Remark 3.2 to precisely address this issue.}

\item In Numerical Simulation, the authors can add some time responses of
the original and reduced-order models.	For example, showing impulse
responses of the models enables readers to understand "practical"
importance of the proposed method.\\
\serkan{\textsf{AR}:  We have added a graph showing the time responses for the error for different methods; Figure 4 in the revised version. We have chosen to include the impulse error plot instead of the impulse responses to better illustrate the deviations.  Due to the page limit stated by Automatica, we were able to include only one such figure. For a reference, we are including  two additional graphs here.}
 \begin{figure}[H]
 \centering
   \includegraphics [scale=0.5]{absHeatErrorYlim}
      \caption{POD vs \FH for the heat model\label{fig:impulseHeat}}
 \end{figure}
 \begin{figure}[H]
 \centering
   \includegraphics [scale=0.5]{absUNSError}
      \caption{POD vs \FH for the unstable model\ \label{fig:impulseUns}}
 \end{figure}

### 2019-05-13 FH Optimality Conditions Paper.tex
Latest SG Changes

\end{frontmatter}
%Introduction
%Introduction
\section{Introduction}
%Simulation, design, and control of dynamical systems play an important role in numerous scientific and industrial tasks such as signal propagation in the nervous system\cite{kellems2009low}, heat dissipation, prediction of major weather events \cite{BoyP11,Sha03,Ant05}. 
Simulation, design, and control of dynamical systems play an important role in numerous scientific and industrial tasks such as \textcolor{red}{signal propagation in the nervous system\cite{kellems2009low};  the synthesis  of
interconnect \cite{BonD07} and semiconductor devices \cite{Hess2014}; large-scale inverse problem,
 \cite{Druskin2011solution,Lieberman2010,de2015nonlinear}; and prediction of major weather events \cite{Ant05}.}
The need for  detailed  models due to the increasing demand for greater resolution leads to  
large-scale dynamical systems, posing tremendous computational difficulties when applied in numerical simulations. In order to overcome these challenges, we perform  model reduction where we replace the large-scale dynamics with high-fidelity reduced representations.

@@

\textcolor{red}{In this paper,  we explore optimal model reduction over a finite time horizon. We use a time-limited version of the $\ch_2$ norm, denoted by $\ch_2(\tf)$, to quantify the model reduction error.}
 Optimality requires a parametrization of the reduced model. We will work with the time-domain representation of the dynamical system to derive the optimality conditions. Specifically, we represent the impulse response of the reduced dynamical system using the modal decomposition, i.e.,
 \begin{equation}\label{kernel}
\begin{aligned}
\h_r(t)=\C_r e^{\A_r t}\B_r=\sum_{i=1}^r e^{\lambda_it}\lc_i\rc_i^T.
\end{aligned}
\end{equation}
where $\lambda_i$'s are the eigenvalues of $\A_r$, and $\lc_i \in \CC^{p\times 1}, \rc_i\in \CC^{m\times1}$. 
In other words, the impulse response is expressed as a sum of $r$ rank-1 $p\times m$  matrices.
To simplify the presentation,  we assume  that $\lambda_i$'s, the reduced order poles,  are simple.  The representation \eqref{kernel} 
is nothing but a state-space transformation on $\h_r(t)=\C_r e^{\A_r t}\B_r$ using the eigenvectors of $\A_r$. 
Using the parametrization of the reduced model in \eqref{kernel}, we derive interpolatory optimality conditions in the $\ch_2(\tf)$ norm and implement a model reduction algorithm that satisfies these optimality conditions.

\textcolor{red}{The advantage of the interpolation framework we will develop  is that 
we do not require the reduced-model to be obtained via projection, as usually assumed in model reduction \cite{Ant05}. Indeed, one observation we will make is that unlike in the infinite-horizon $\ch_2$ approximation problem, the optimal reduced model in the finite-horizon norm is not necessarily given by a projection and thus a projection-based approach will not be able to satisfy the optimality conditions. Therefore,  
by treating the poles and residues in \eqref{kernel} as the parameters and directly working with them, we  obtain a reduced model to satisfy the optimality conditions exactly.}

@@

%Interpolatory Model Reduction
\subsection{Interpolatory Conditions for Optimal $\ch_2$ Model Reduction}
Given a reduced order $r$, the goal is to construct a reduced order model whose transfer function $\HH_r(s)$ minimizes the $\ch_2$ error norm $\norm{\HH - \HH_r}_{\ch_2}$.  Since this is a non-convex optimization problem, the usual, numerically feasible, approach  is to find a reduced model that satisfies the necessary conditions for $\ch_2$ optimality. These conditions can be formulated in terms of Sylvester equations \cite{Wil70,HylB85} or interpolation \cite{MeiL67,GugBA08}. These two frameworks are equivalent \cite{GugBA08}. In this paper, we will focus on the interpolation framework.
\begin{theorem} \label{h2thm}%{\text{\cite {MeiL67, GugBA08}}}
Let 
$$
\h_r(t)=\sum_{k=1}^r e^{\lambda_kt}\lc_k\rc_k^T \qquad \Longleftrightarrow \qquad \HH_r(s) = \sum_{k=1}^r \frac{\lc_k\rc_k^T}{s-\lambda_k}
$$
be the best $r^{th}$ order approximation of an asymptotically stable linear dynamical system  $\HH(s)$ with respect to the $\ch_2$ norm. Then, for $k=1, 2, ... , r$,
\begin{equation} \label{eqn:h2cond}
\begin{aligned}
\lc_k^T\HH(-\lambda_k)&=\lc_k^T\HH_r(-\lambda_k),\\~~
\HH(-\lambda_k)\rc_k&=\HH_r(-\lambda_k)\rc_k,\\
\lc_k^T\HH'(-\lambda_k)\rc_k&=\lc_k^T\HH_r'(-\lambda_k)\rc_k.
\end{aligned}
\end{equation}
\end{theorem}
{\color{red}For more details on theorem \ref{h2thm}, see {\cite {GugBA08}}.}
This result states that the transfer function of the optimal $\ch_2$ approximation to $\HH(s)$ is a (tangential) Hermite interpolant where the interpolation points are the mirror images of the reduced-order poles $\{\lambda_k\}$, and the tangental directions are given by the corresponding residues $\{\lc_k\rc_k^T\}$. {\color{red} Throughout this paper, we denote the derivative of $\HH(s)$ by $\HH'(s)$.} Since the optimality conditions depend on the reduced-model to be computed, the solution requires a nonlinear iteration. The Iterative Rational Krylov Algorithm (IRKA)  \cite{GugBA08} and its variants such as \cite{beattie2012realization,gerstner2007hom,CasL18,beattie2009trust} use these interpolation based optimality conditions to produce   an interpolatory, locally $\ch_2$ optimal reduced model. The next section will extend this framework to the finite-time interval case.

%FH model reduction
\section{$\ch_2(\tf)$ Optimal Model Reduction on a Finite Horizon}  \label{sec:main} 
%If we are interested  in the behavior of a system only in a finite time interval (or access to a numerical simulation only on a finite time interval), we can obtain better reduced models by defining the measure of approximation quality over the interval of interest, instead of  focussing on the infinite time horizon. 
%
{\color{red}
In this section, we present  the main theoretical results of the paper i.e., the interpolatory $\ch_2(\tf)$  optimality conditions, and discuss their implications.}

@@

%Error measures in a finite-time horizon
\subsection{$\ch_2(t_f)$ Norm on a Finite-time Horizon}
It is immediately clear from the time-domain definition of the (infinite-horizon) $\ch_2$ norm how to define the finite-horizon version:
\begin{Definition}\label{innerh2}
Let $\h(t)$ and $\g(t)$ denote the impulse responses of two dynamical systems with real state-space realizations.  
For a finite-time horizon 
$[0,t_f]$, the $\ch_2(\tf)$\footnote{\textcolor{red}{Even though we are using an error measure specifically formulated in the time domain,   following \cite{RedK17,GoyR17} we choose to use  the $\ch_2(\tf)$ notation, despite the term $\ch_2$  is mostly associated with a measure defined in the frequency domain. Our main reason is to keep the connection to the infinite horizon problem where the measure in the frequency- and time-domains are equivalent. And more importantly, as in the regular $\ch_2$ case, the optimality conditions will still appear as interpolation conditions in the frequency domain. 
 %In the Since the time domain and frequency domain functions are equivalent,  this notation is appropriate. Furthermore, since the infinite horizon, and finite horizon case appear to be connected, the notation $\mathcal{H}_2(t_f)$ illustrates this connection. \cite{RedK17,GoyR17} use similar notation.
 }}
   inner product $\langle \cdot, \cdot \rangle_{\ch_2(\tf)}$ 
and $\ch_2(\tf)$ norm $\norm{\cdot}_{\ch_2(\tf)}$ are defined as  
\begin{align*}
\langle \h, \g \rangle_{\ch_2(\tf)} &=\int_0^{\tf} \mathsf{Tr}( (\h(t))^T \g(t)) dt, \\%\quad \mbox{and}\quad
\norm{\h}_{\ch_2(\tf)} &=\sqrt{\int_0^{\tf} \norm{\h(t)}_F^2 dt}.
\end{align*}

@@

%%Remark 3.2
%\begin{remark}
%Before we prove Theorem \ref{mh2opt}, we briefly comment on its implications. In the infinite-horizon case, if $\HH_r(s)$ is the best $\ch_2$ approximation to $\HH(s)$, then $\HH_r(s)$ interpolates $\HH(s)$. However, in the finite-horizon case, 
%the interpolant is $\G_r(s)$, which is a function of $\HH_r(s)$, and the interpolated function is $\G(s)$, which is a function of $\HH(s)$; thus $\HH_r(s)$ does not interpolate $\HH(s)$ in this case. However, the optimal interpolation points  and directions are still determined by the reduced model $\HH_r(s)$. The algorithmic implications of this result will be revisited in Section \ref{sec:discuss}.
%\end{remark}
The next lemma will be used in proving Theorem \ref{mh2opt}.
\begin{Lemma}\label{mgexp}
Let $\G(s)$ and $\G_r(s)$ be as defined in \eqref{eqn:defG} and \eqref{eqn:defGr}, respectively. Then,
\begin{align}
\G(-\lambda_k)&=\phantom{-}\sum_{j=1}^n\cc_j\bb_j^T\dfrac{e^{(\lambda_k+\rho_j){\tf}}-1}{\lambda_k+\rho_j},
\label{eqn:Gatlk}\\
 \G'(-\lambda_k)& =-\sum_{j=1}^n\cc_i\bb_i^T\dfrac {({\tf} (\lambda_k+\rho_j)-1)e^{(\lambda_k+\rho_j){\tf}}+1}{(\lambda_k+\rho_j)^2}, \label{eqn:Gpatlk}  \\
 \G_r(-\lambda_k)&=\phantom{-}\sum_{j=1}^n\lc_j\rc_j^T\dfrac{e^{(\lambda_k+\lambda_j){\tf}}-1}{\lambda_k+\lambda_j}, ~~\mbox{and} 
\label{eqn:Gratlk}\\
 \G_r'(-\lambda_k)& =-\sum_{j=1}^n\lc_j\rc_j^T\dfrac {({\tf} (\lambda_k+\lambda_j)-1)e^{(\lambda_k+\lambda_i){\tf}}+1}{(\lambda_k+\lambda_j)^2}. \label{eqn:Grpatlk} 
\end{align}
\end{Lemma}
\begin{pf}
Recall the definition of $\G(s) = -e^{-s\tf}\C(s\I-\A)^{-1}e^{\A \tf}\B+\HH(s)$. Note that we assume that the eigenvalues of $\A$ are simple. Therefore, $e^{\A \tf}$ is also diagonalizable by the eigenvectors of $\A$. Using this fact and the pole-zero residue decomposition of   $\HH(s) = \C(s\I-\A)^{-1} \B = \sum_{j=1}^n \frac{\cc_j \bb_j^T}{s-\rho_j}$, we obtain 
\begin{align}
\G(s) &= -e^{-s\tf}\C(s\I-\A)^{-1}e^{\A \tf}\B+\HH(s)  \nonumber \\ 
&=-e^{-s{\tf}}\sum_{j=1}^n\cc_j\bb_j^T\dfrac{e^{\rho_j\tf}}{s-\rho_j}+\sum_{j=1}^n\cc_j\bb_j^T\dfrac{1}{s-\rho_j}\\
&=\sum_{j=1}^n\cc_j\bb_j^T\dfrac{-e^{(-s + \rho_j){\tf}}}{s-\rho_j}+\sum_{j=1}^n\cc_j\bb_j^T\dfrac{1}{s-\rho_j} \nonumber\\
&=\sum_{j=1}^n\cc_j\bb_j^T\dfrac{e^{(-s+\rho_j)\tf}-1}{-s+\rho_j}. \label{eq:Gs}
\end{align}
Thus,
$\G(-\lambda_k)=\sum_{j=1}^n\cc_j\bb_j^T\dfrac{e^{(\lambda_k+\rho_j){\tf}}-1}{\lambda_k+\rho_j}$,
which proves \eqref{eqn:Gatlk}. To prove \eqref{eqn:Gpatlk}, we first differentiate \eqref{eq:Gs} with respect to $s$ to obtain
 \G'(s) =\sum_{j=1}^n\cc_j\bb_j^T\dfrac {{\tf} (s-\rho_j)e^{(-s+\rho_j){\tf}}+e^{(-s+\rho_j){\tf}}-1}{(s-\rho_j)^2}
 Plugging in $s= -\lambda_k$ in this last expression yields the desired result \eqref{eqn:Gpatlk}. The proofs of
 \eqref{eqn:Gpatlk} and \eqref{eqn:Grpatlk} follow analogously. 
\end{pf}%%%Start proof here

@@

{\color{red}

@@

 \begin{figure}[H] 
 \centering
 \includegraphics [scale=0.35]{fig1h} 
 \caption{\FH \ and other algorithms for a heat model\label{fig:hm}}
 \end{figure}
 \begin{figure}[H]
 \centering
  \includegraphics [scale=0.35]{fig2i}
 \caption{\FH \ and other algorithms for the heat model \label{fig:iss}}
 \end{figure}
  \begin{figure}[H]
 \centering
   \includegraphics [scale=0.35]{fig3u}
      \caption{\FH \ and other algorithms for the ISS model \label{fig:uns}}
 \end{figure}

 \begin{figure}[H]
 \centering
   \includegraphics [scale=0.35]{ISS1RErrorSmooth}
      \caption{\FH \ and other algorithms for the unstable model \label{fig:impulse}}
 \end{figure}

>>>>

\end{frontmatter}
%Introduction
%Introduction
\section{Introduction}
%Simulation, design, and control of dynamical systems play an important role in numerous scientific and industrial tasks such as signal propagation in the nervous system\cite{kellems2009low}, heat dissipation, prediction of major weather events \cite{BoyP11,Sha03,Ant05}. 
Simulation, design, and control of dynamical systems play an important role in numerous scientific and industrial tasks such as \textcolor{blue}{signal propagation in the nervous system\cite{kellems2009low};  the synthesis  of
interconnect \cite{BonD07} and semiconductor devices \cite{Hess2014}; large-scale inverse problem,
 \cite{Druskin2011solution,Lieberman2010,de2015nonlinear}; and prediction of major weather events \cite{Ant05}.}
The need for  detailed  models due to the increasing demand for greater resolution leads to  
large-scale dynamical systems, posing tremendous computational difficulties when applied in numerical simulations. In order to overcome these challenges, we perform  model reduction where we replace the large-scale dynamics with high-fidelity reduced representations.

@@

\textcolor{blue}{In this paper,  we explore optimal model reduction over a finite time horizon. We use a time-limited version of the $\ch_2$ norm, denoted by $\ch_2(\tf)$, to quantify the model reduction error.}
 Optimality requires a parametrization of the reduced model. We will work with the time-domain representation of the dynamical system to derive the optimality conditions. Specifically, we represent the impulse response of the reduced dynamical system using the modal decomposition, i.e.,
 \begin{equation}\label{kernel}
\begin{aligned}
\h_r(t)=\C_r e^{\A_r t}\B_r=\sum_{i=1}^r e^{\lambda_it}\lc_i\rc_i^T.
\end{aligned}
\end{equation}
where $\lambda_i$'s are the eigenvalues of $\A_r$, and $\lc_i \in \CC^{p\times 1}, \rc_i\in \CC^{m\times1}$. 
In other words, the impulse response is expressed as a sum of $r$ rank-1 $p\times m$  matrices.
To simplify the presentation,  we assume  that $\lambda_i$'s, the reduced order poles,  are simple.  The representation \eqref{kernel} 
is nothing but a state-space transformation on $\h_r(t)=\C_r e^{\A_r t}\B_r$ using the eigenvectors of $\A_r$. 
Using the parametrization of the reduced model in \eqref{kernel}, we derive interpolatory optimality conditions in the $\ch_2(\tf)$ norm and implement a model reduction algorithm that satisfies these optimality conditions.

\textcolor{blue}{The advantage of the interpolation framework we will develop  is that 
we do not require the reduced-model to be obtained via projection, as usually assumed in model reduction \cite{Ant05}. Indeed, one observation we will make is that unlike in the infinite-horizon $\ch_2$ approximation problem, the optimal reduced model in the finite-horizon norm is not necessarily given by a projection and thus a projection-based approach will not be able to satisfy the optimality conditions. Therefore,  
by treating the poles and residues in \eqref{kernel} as the parameters and directly working with them, we  obtain a reduced model to satisfy the optimality conditions exactly.}

@@

%Interpolatory Model Reduction
\subsection{Interpolatory Conditions for Optimal $\ch_2$ Model Reduction}
Given a reduced order $r$, the goal is to construct a reduced order model whose transfer function $\HH_r(s)$ minimizes the $\ch_2$ error norm $\norm{\HH - \HH_r}_{\ch_2}$.  Since this is a non-convex optimization problem, the usual, numerically feasible, approach  is to find a reduced model that satisfies the necessary conditions for $\ch_2$ optimality. These conditions can be formulated in terms of Sylvester equations \cite{Wil70,HylB85} or interpolation \cite{MeiL67,GugBA08}. These two frameworks are equivalent \cite{GugBA08}. In this paper, we will focus on the interpolation framework.
\begin{theorem} \label{h2thm}%{\text{\cite {MeiL67, GugBA08}}}
Let 
$$
\h_r(t)=\sum_{k=1}^r e^{\lambda_kt}\lc_k\rc_k^T \qquad \Longleftrightarrow \qquad \HH_r(s) = \sum_{k=1}^r \frac{\lc_k\rc_k^T}{s-\lambda_k}
$$
be the best $r^{th}$ order approximation of an asymptotically stable linear dynamical system  $\HH(s)$ with respect to the $\ch_2$ norm. Then, for $k=1, 2, ... , r$,
\begin{equation} \label{eqn:h2cond}
\begin{aligned}
\lc_k^T\HH(-\lambda_k)&=\lc_k^T\HH_r(-\lambda_k),\\~~
\HH(-\lambda_k)\rc_k&=\HH_r(-\lambda_k)\rc_k,\\
\lc_k^T\HH'(-\lambda_k)\rc_k&=\lc_k^T\HH_r'(-\lambda_k)\rc_k.
\end{aligned}
\end{equation}
\end{theorem}
{\color{blue} where $\HH'(s)$ denotes the derivative of $\HH(s)$ with respect to $s$.}
{\color{blue}For more details on Theorem \ref{h2thm}, see {\cite {GugBA08,AntBG10b}}.}
This result states that the transfer function of the optimal $\ch_2$ approximation to $\HH(s)$ is a (tangential) Hermite interpolant where the interpolation points are the mirror images of the reduced-order poles $\{\lambda_k\}$, and the tangental directions are given by the corresponding residues $\{\lc_k\rc_k^T\}$.  Since the optimality conditions depend on the reduced-model to be computed, the solution requires a nonlinear iteration. The Iterative Rational Krylov Algorithm (IRKA)  \cite{GugBA08} and its variants such as \cite{beattie2012realization,gerstner2007hom,CasL18,beattie2009trust} use these interpolation based optimality conditions to produce   an interpolatory, locally $\ch_2$ optimal reduced model. The next section will extend this framework to the finite-time interval case.

%FH model reduction
\section{$\ch_2(\tf)$ Optimal Model Reduction on a Finite Horizon}  \label{sec:main} 
%If we are interested  in the behavior of a system only in a finite time interval (or access to a numerical simulation only on a finite time interval), we can obtain better reduced models by defining the measure of approximation quality over the interval of interest, instead of  focussing on the infinite time horizon. 
%
{\color{blue}
In this section, we present  the main theoretical results of the paper i.e., the interpolatory $\ch_2(\tf)$  optimality conditions, and discuss their implications.}

@@

%Error measures in a finite-time horizon
\subsection{$\ch_2(t_f)$ Norm on a Finite-time Horizon}
It is immediately clear from the time-domain definition of the (infinite-horizon) $\ch_2$ norm how to define the finite-horizon version:
\begin{Definition}\label{innerh2}
Let $\h(t)$ and $\g(t)$ denote the impulse responses of two dynamical systems with real state-space realizations.  
For a finite-time horizon 
$[0,t_f]$, the $\ch_2(\tf)$\footnote{\textcolor{blue}{Even though we are using an error measure specifically formulated in the time domain,   following \cite{RedK17,GoyR17} we choose to use  the $\ch_2(\tf)$ notation, despite the term $\ch_2$  is mostly associated with a measure defined in the frequency domain. Our main reason is to keep the connection to the infinite horizon problem where the measure in the frequency- and time-domains are equivalent. And more importantly, as in the regular $\ch_2$ case, the optimality conditions will still appear as interpolation conditions in the frequency domain. 
 %In the Since the time domain and frequency domain functions are equivalent,  this notation is appropriate. Furthermore, since the infinite horizon, and finite horizon case appear to be connected, the notation $\mathcal{H}_2(t_f)$ illustrates this connection. \cite{RedK17,GoyR17} use similar notation.
 }}
   inner product $\langle \cdot, \cdot \rangle_{\ch_2(\tf)}$ 
and $\ch_2(\tf)$ norm $\norm{\cdot}_{\ch_2(\tf)}$ are defined as  
\begin{align*}
\langle \h, \g \rangle_{\ch_2(\tf)} &=\int_0^{\tf} \mathsf{Tr}( (\h(t))^T \g(t)) dt, \\%\quad \mbox{and}\quad
\norm{\h}_{\ch_2(\tf)} &=\sqrt{\int_0^{\tf} \norm{\h(t)}_F^2 dt}.
\end{align*}

@@

%%Remark 3.2
%\begin{remark}
%Before we prove Theorem \ref{mh2opt}, we briefly comment on its implications. In the infinite-horizon case, if $\HH_r(s)$ is the best $\ch_2$ approximation to $\HH(s)$, then $\HH_r(s)$ interpolates $\HH(s)$. However, in the finite-horizon case, 
%the interpolant is $\G_r(s)$, which is a function of $\HH_r(s)$, and the interpolated function is $\G(s)$, which is a function of $\HH(s)$; thus $\HH_r(s)$ does not interpolate $\HH(s)$ in this case. However, the optimal interpolation points  and directions are still determined by the reduced model $\HH_r(s)$. The algorithmic implications of this result will be revisited in Section \ref{sec:discuss}.
%\end{remark}
The next lemma will be used in proving Theorem \ref{mh2opt}.
\begin{Lemma}\label{mgexp}
Let $\G(s)$ and $\G_r(s)$ be as defined in \eqref{eqn:defG} and \eqref{eqn:defGr}, respectively. Then,
\begin{align}
\G(-\lambda_k)&=\phantom{-}\sum_{j=1}^n\cc_j\bb_j^T\dfrac{e^{(\lambda_k+\rho_j){\tf}}-1}{\lambda_k+\rho_j},
\label{eqn:Gatlk}\\
 \G'(-\lambda_k)& =-\sum_{j=1}^n\cc_i\bb_i^T\dfrac {({\tf} (\lambda_k+\rho_j)-1)e^{(\lambda_k+\rho_j){\tf}}+1}{(\lambda_k+\rho_j)^2}, \label{eqn:Gpatlk}  \\
 \G_r(-\lambda_k)&=\phantom{-}\sum_{j=1}^n\lc_j\rc_j^T\dfrac{e^{(\lambda_k+\lambda_j){\tf}}-1}{\lambda_k+\lambda_j}, ~~\mbox{and} 
\label{eqn:Gratlk}\\
 \G_r'(-\lambda_k)& =-\sum_{j=1}^n\lc_j\rc_j^T\dfrac {({\tf} (\lambda_k+\lambda_j)-1)e^{(\lambda_k+\lambda_i){\tf}}+1}{(\lambda_k+\lambda_j)^2}. \label{eqn:Grpatlk} 
\end{align}
\end{Lemma}
\begin{pf}
Recall the definition of $\G(s) = -e^{-s\tf}\C(s\I-\A)^{-1}e^{\A \tf}\B+\HH(s)$. Note that we assume that the eigenvalues of $\A$ are simple. Therefore, $e^{\A \tf}$ is also diagonalizable by the eigenvectors of $\A$. Using this fact and the pole-zero residue decomposition of   $\HH(s) = \C(s\I-\A)^{-1} \B = \sum_{j=1}^n \frac{\cc_j \bb_j^T}{s-\rho_j}$, we obtain 
\begin{align}
\G(s) &= -e^{-s\tf}\C(s\I-\A)^{-1}e^{\A \tf}\B+\HH(s)  \nonumber \\ 
&=-e^{-s{\tf}}\sum_{j=1}^n\cc_j\bb_j^T\dfrac{e^{\rho_j\tf}}{s-\rho_j}+\sum_{j=1}^n\cc_j\bb_j^T\dfrac{1}{s-\rho_j}\\
&=\sum_{j=1}^n\cc_j\bb_j^T\dfrac{-e^{(-s + \rho_j){\tf}}}{s-\rho_j}+\sum_{j=1}^n\cc_j\bb_j^T\dfrac{1}{s-\rho_j} \nonumber\\
&=\sum_{j=1}^n\cc_j\bb_j^T\dfrac{e^{(-s+\rho_j)\tf}-1}{-s+\rho_j}. \label{eq:Gs}
\end{align}
Thus,
$\G(-\lambda_k)=\sum_{j=1}^n\cc_j\bb_j^T\dfrac{e^{(\lambda_k+\rho_j){\tf}}-1}{\lambda_k+\rho_j}$,
which proves \eqref{eqn:Gatlk}. To prove \eqref{eqn:Gpatlk}, we first differentiate \eqref{eq:Gs} with respect to $s$ to obtain
 \begin{align*}
 \G'(s) =\sum_{j=1}^n\cc_j\bb_j^T\dfrac {{\tf} (s-\rho_j)e^{(-s+\rho_j){\tf}}+e^{(-s+\rho_j){\tf}}-1}{(s-\rho_j)^2}
 \end{align*}
 Plugging in $s= -\lambda_k$ in this last expression yields the desired result \eqref{eqn:Gpatlk}. The proofs of
 \eqref{eqn:Gpatlk} and \eqref{eqn:Grpatlk} follow analogously. 
\end{pf}%%%Start proof here

@@

{\color{blue}

@@

 \begin{figure}[H]
 \centering
  \includegraphics [scale=0.35]{fig2i}
 \caption{\FH \ and other algorithms for the heat model \label{fig:iss}}
 \end{figure}
  \begin{figure}[H]
 \centering
   \includegraphics [scale=0.35]{fig3u}
      \caption{\FH \ and other algorithms for the unstable model \label{fig:uns}}
 \end{figure}

\textcolor{blue}{Finally, in Figure \ref{fig:impulse}, we compare the error in the impulse responses due to POD and \FH \ for the ISS model. For both methods, POD and \FH\  the reduced model was of order $r=14$. As we can see from the graph, \FH \ clearly outperforms POD on the time interval $[0, 1]$.}

 \begin{figure}[H]
 \centering
   \includegraphics [scale=0.35]{ISS1RErrorSmooth}
      \caption{\FH \ and POD for the ISS 1R model \label{fig:impulse}}
 \end{figure}
